---
title: "Multilevel binomial regression"
output: html_notebook
---
```{r}
library(lme4) 
library(dplyr)
```


```{r}
df = read.csv("final.csv")
```

```{r}
# convert categorical variables to factors
df$gender <- as.factor(df$gender)
df$parliamentary_group <- as.factor(df$parliamentary_group)
df$Hate_score <- as.factor(df$Hate_score)
df$Sentiment <- as.factor(df$Sentiment)
```

This model is a Generalized Linear Mixed Effects Model (GLMM) that is used to predict the Hate_score (1 = Hateful, 0 = Non Hateful) based on the following independent variables:

- Sentiment: sentiment of the tweet published by the politician
- followers_count: followers count of the politician
- gender: gender of the politician
- parliamentary_group: parliamentary group of the politician

The model includes a random effect term (1 | source_tweet), which means that the intercept for the dependent variable (Hate_score) is allowed to vary for each unique source_tweet. This accounts for the fact that the mean of the dependent variable may differ between different source_tweets. The family argument is set to "binomial" because the dependent variable is binary (1 or 0).

```{r}
fit <- glmer(Hate_score ~ Sentiment + 
               gender + 
               parliamentary_group + 
               (1 | Tweet_ID), 
             data = df, 
             family = binomial())
```

```{r}
summary(fit)
```

